The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
weak lensing should not in general be capitalized

In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
In studies of Weak Lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
This is done by comparing the 1-D redshift distribution to some of the parametric models available in the literature. 
The incompleteness in the sample is minimized by constructing a volume limited sample either by imposing stellar mass cuts (\s$3$) or by imposing a luminosity cut. 
Further, depending on whether we have the cut fixed or evolve with redshift, we get two more volume limited samples \s$1$ and \s$2$ respectively. 
Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic indices and \btt ratios.

@@

Our result has serious implications for realistic image simulations for Weak Lensing. 
It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 
This is particularly a problem with narrow surveys where a single galaxy cluster or a void could affect the environment significantly. 
Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST_Book} will image larger areas of sky mitigating the dependence of local environment in image simulations.

>>>>

In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect weak lensing simulations.
In studies of weak lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
This is done by comparing the 1-D redshift distribution to some of the parametric models available in the literature. 
The incompleteness in the sample is minimized by constructing a volume limited sample either by imposing stellar mass cuts (\s$3$) or by imposing a luminosity cut. 
Further, depending on whether we have the cut fixed or evolve with redshift, we get two more volume limited samples \s$1$ and \s$2$ respectively. 
Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic indices and \btt ratios.

@@

Our result has serious implications for realistic image simulations for weak lensing. 
It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 
This is particularly a problem with narrow surveys where a single galaxy cluster or a void could affect the environment significantly. 
Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST_Book} will image larger areas of sky mitigating the dependence of local environment in image simulations.
